### 2018-03-07 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Loci Up to Date

\documentclass{article}[18pt]
\usepackage[dvipsnames]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{tabularx}

@@

\subsection{$\mathbf{|z-z_1|=r}$}

@@

           \node[anchor=west] (source) at (axis cs:1,2){};
       \node (destination) at (axis cs:3,4.5){};
       \draw[->](source)--(destination);
\end{axis}
\end{tikzpicture}
\subsection{$\mathbf{|z-z_1|=|z-z_2|}$}
$|z-z_1|=|z-z_2|$ is represented by a perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\\
To find the Cartesian form, replace z with $x+iy$ and expand, squaring both sides to remove the modulus signs.\\
\\
This looks like the graph:\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

@@

\end{axis}
\end{tikzpicture}\\
For cases where there is a constant in front of one of the modulus signs, use the algebraic method to find the Cartesian form, then plot that.
\newpage
\subsection{$\mathbf{\arg(z-z_1)=\theta}$}
$\arg(z-z_1)=\theta$ is represented by the half-line from the fixed point $z_1$, making an angle $\theta$ with a line from the fixed point $z_1$, parallel to the real axis.\\
\\
To find the Cartesian form, replace z with $x+iy$ and separate into the real and imaginary parts. Then use the trigonometric identity $\tan\theta=\dfrac{\textrm{Opposite}}{\textrm{Adjacent}}$ and simplify.\\
\\
When plotting remember that $\theta$ is the angle anticlockwise.\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

@@

\end{axis}
\end{tikzpicture}
\subsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
$\mathlarger{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}$ represents an arc anticlockwise between $z_1$ and $z_2$

\end{document}

>>>>

\documentclass{article}[18pt]
\usepackage[dvipsnames]{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{tabularx}

@@

\subsection{Lines}
\subsubsection{$\mathbf{|z-z_1|=r}$}

@@

           \node[anchor=west] (source) at (axis cs:1,2){};
       \node (destination) at (axis cs:3,4.5){};
       \draw[->](source)--(destination);
\end{axis}
\end{tikzpicture}
\subsubsection{$\mathbf{|z-z_1|=|z-z_2|}$}
$|z-z_1|=|z-z_2|$ is represented by a perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\\
To find the Cartesian form, replace z with $x+iy$ and expand, squaring both sides to remove the modulus signs.\\
\\
This looks like the graph:\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

@@

\end{axis}
\end{tikzpicture}\\
For cases where there is a constant in front of one of the modulus signs, use the algebraic method to find the Cartesian form, then plot that.
\newpage
\subsubsection{$\mathbf{\arg(z-z_1)=\theta}$}
$\arg(z-z_1)=\theta$ is represented by the half-line from the fixed point $z_1$, making an angle $\theta$ with a line from the fixed point $z_1$, parallel to the real axis.\\
\\
To find the Cartesian form, replace z with $x+iy$ and separate into the real and imaginary parts. Then use the trigonometric identity $\tan\theta=\dfrac{\textrm{Opposite}}{\textrm{Adjacent}}$ and simplify.\\
\\
When plotting remember that $\theta$ is the angle anticlockwise.\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

@@

\end{axis}
\end{tikzpicture}
\subsubsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
$\mathlarger{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}$ represents an arc anticlockwise between $z_1$ and $z_2$
\subsection{Regions}
\subsubsection{$\mathbf{|z-(2+3i)|\leqslant3}$}
This is the area inside the circle represented by $|z-(2+3i)|\leqslant3$\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

\filldraw[gray,opacity=0.6] (axis cs:1,2) circle [black, radius=3];
\draw (axis cs:1,2) circle [black, radius=3];
\end{axis}
\end{tikzpicture}
\newpage
\subsubsection{$\mathbf{|z-3|<|z-5|}$}
This is the area to one side of the perpendicular bisector represented equal to $|z-3|=|z-5|$\\
\pgfplotsset{compat=newest}

\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,xtick={3,4,5}, ytick={0},ytick pos=right]
\addplot coordinates { (4,-5) (4,5) };
\filldraw [gray,opacity=0.6] (-5,-5) rectangle (4,5);
\end{axis}
\end{tikzpicture}
\subsubsection{$\mathbf{0\leqslant\arg(z-2)<\frac{\pi}{4}}$}
This is the area between the positive real axis and the half line equal to $\arg(z-2)=\frac{\pi}{4}$\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,xtick={2}, ytick={0},ytick pos=right]
\addplot coordinates { (2,0) (5,3) };
\filldraw[gray,opacity=0.6] (2,0) -- (5,0) -- (5,3) -- cycle;

\end{axis}
\end{tikzpicture}
\end{document}
